Landscape composition and beneficial insects

### 2020-06-10 manuscript/manuscript_outline.Rmd
Added reference

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, p[loc=='Pivot'])`, `r with(opilLinTerms, p[loc=='Wetland'])`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`)
  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`, `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
  + The temporal and spatial components, as in the other two species, were both very strong (both p = `r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
  + Together, these results indicate that _P. opilio_ activity density is influenced by large-scale geographic patterns rather than landscape composition
  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of deviance

>>>>

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, p[loc=='Pivot'])`, `r with(opilLinTerms, p[loc=='Wetland'])`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`)
  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`, `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
  + The temporal and spatial components, as in the other two species, were both very strong (both p = `r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
  + Together, these results indicate that _P. opilio_ activity density is influenced by large-scale geographic patterns rather than landscape composition
  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance
